\documentclass[../main.tex]{subfile}

\begin{document}

\section{Results \& Discussion} \label{sec:results-&-discussion}
    
    In this section, we will present the results of the combination between the various imaging representation methods, their appropriate neural network architectures, and a Gabor Filter. Experiments were made using all of the six fruits separately, they can be seen in \Cref{fig:abius,fig:cajus-amarelos,fig:cajus-vermelhos,fig:gabirobas,fig:pequis,fig:siriguelas}.
    
    \subfile{../figures/fruits/abiu}
    \subfile{../figures/fruits/caju-amarelo}
    \subfile{../figures/fruits/caju-vermelho}
    \subfile{../figures/fruits/gabiroba}
    \subfile{../figures/fruits/pequi}
    \subfile{../figures/fruits/siriguela}
    
    Across all the graphs, the y-axis represents the accuracies (training and validation) achieved by the model, while the x-axis represents the epochs from when the models were being trained. Those models were trained for different epochs, due to a technique called Early Stopping, which stops the training when there is no improvement in loss, which is a measure of how wrong a model is, for a number of consecutive epochs.
    
    Analyzing the graphs, it is clear that the GLCM textural properties-based models outran the image-based ones. Between the image-based models, the ones that used RGB images managed to be slightly better in general. It is also visible a strange behavior on various graphs. It tends to occur more often in the GLCM based models. And this strange behavior is when a model achieved better results on the validation set. A possible explanation is when the validation set is too easy, which is completely plausible due to the small datasets used.
    
    \subfile{../tables/fruits-comparison}
    
    A closer look at the best results across all the fruits, i.e., GLCM textural properties with a DNN, can be seen in Table \ref{tab:fruits-comparison}. First of all, it is safe to assume the results were overall great, since every result is above 95\%, except for the \textit{pequi} fruit. And the \textit{siriguela} fruit was the one that achieved the best accuracies on both training and validation environments. Aside from that, between all the graphs, the graphs drawn from \textit{siriguelas} have more consistent and smoother lines.

\end{document}